Hypertension and microbiome

### 2019-06-07 articletwo.Rmd
Typo

```{r top generas, eval = FALSE, include = FLASE}
abund.genus <- abundances(pseq.genus, transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

>>>>

```{r top generas, eval = FALSE, include = FALSE}
abund.genus <- abundances(pseq.genus, transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))
